---
title: "R Graphics Cookbook Chapter 3"
author: "Bowen Jones"
date: "`r Sys.Date()`"
output: html_document
---

### Chapter 3. Bar Graphs

```{r}
library(ggplot2)
library(gcookbook)
```

### Section 3.1. Making a Basic Bar Graph

```{r}
# Figure 3-1
 ggplot(pg_mean, aes(group, weight)) +
  geom_bar(stat="identity")

# Figure 3-2
ggplot(BOD, aes(Time, demand)) +
  geom_bar(stat = "identity")
ggplot(BOD, aes(factor(Time), demand)) +
  geom_bar(stat = "identity")

# Figure 3-3
ggplot(pg_mean, aes(group, weight)) +
  geom_bar(stat="identity", fill = "lightblue", color = "black")
```

### Section 3.2. Grouping Bars Together
```{r}
# Figure 3-4
ggplot(cabbage_exp, aes(x=Date, y=Weight, fill = Cultivar)) +
  geom_bar(position = "dodge", stat="identity")

# Figure 3-5
ggplot(cabbage_exp, aes(Date, Weight, fill = Cultivar)) +
  geom_bar(position = "dodge", color = "black", stat = "identity") +
  scale_fill_brewer(palette="Pastel1")

# Figure 3-6
ce <- cabbage_exp[1:5, ]
ggplot(ce, aes(Date, Weight, fill = Cultivar)) +
  geom_bar(position = "dodge", color = "black", stat = "identity") +
  scale_fill_brewer(palette="Pastel1")
```

### Section 3.3. Making a Bar Graph of Counts

```{r}
# Figure 3-7
ggplot(diamonds, aes(cut)) +
  geom_bar()

# Figure 3-8
ggplot(diamonds, aes(carat)) +
  geom_bar()
```

### Section 3.4. Using Colors in a Bar Graph

```{r}
upc <- subset(uspopchange, rank(Change)>40)
# Figure 3-9
ggplot(upc, aes(Abb, Change, fill = Region)) +
  geom_bar(stat = "identity")

# Figure 3-10
ggplot(upc, aes(reorder(Abb, Change), Change, fill = Region)) +
  geom_bar(stat="identity", color = "black") +
  scale_fill_manual(values=c("#669933", "#FFCC66")) +
  xlab("State")
```

### Section 3.5. Coloring Negative and Positive Bars Differently

```{r}
csub <- subset(climate, Source=="Berkeley" & Year >= 1900)
csub$pos <- csub$Anomaly10y >= 0

# Figure 3-11
ggplot(csub, aes(Year, Anomaly10y, fill = pos)) +
  geom_bar(stat="identity", position = "identity")

# Figure 3-12
ggplot(csub, aes(Year, Anomaly10y, fill=pos)) +
  geom_bar(stat="identity", position = "identity", color = "black", size = 0.25) +
  scale_fill_manual(values=c("#CCEEFF", "#FFDDDD"), guide=FALSE)
```

### Section 3.6. Adjusting Bar Width and Spacing

```{r}
# Figure 3-13
ggplot(pg_mean, aes(group, weight)) +
  geom_bar(stat="identity")
ggplot(pg_mean, aes(group, weight)) +
  geom_bar(stat="identity", width = 0.5)
ggplot(pg_mean, aes(group, weight)) +
  geom_bar(stat="identity", width=1)

#Figure 3-14
ggplot(cabbage_exp, aes(Date, Weight, fill = Cultivar)) +
  geom_bar(stat = "identity", width = 0.5, position = "dodge")
ggplot(cabbage_exp, aes(Date, Weight, fill = Cultivar)) +
  geom_bar(stat = "identity", width = 0.5, position = position_dodge(0.7))

# Figure 3-15
ggplot(cabbage_exp, aes(Date, Weight, fill = Cultivar)) +
  geom_bar(stat = "identity", width = 0.9, position = position_dodge(0.9))
ggplot(cabbage_exp, aes(Date, Weight, fill = Cultivar)) +
  geom_bar(stat = "identity", width = 0.2, position = position_dodge(0.9))

```

### Section 3.7. Making a Stacked Bar Graph

```{r}
# Figure 3-16
ggplot(cabbage_exp, aes(Date, Weight, fill = Cultivar)) +
  geom_bar(stat="identity")

# Figure 3-17
ggplot(cabbage_exp, aes(Date, Weight, fill = Cultivar)) +
  geom_bar(stat="identity") +
  guides(fill=guide_legend(reverse=TRUE))

# Figure 3-18
library(plyr)
ggplot(cabbage_exp, aes(Date, Weight, fill = Cultivar, order = desc(Cultivar))) +
  geom_bar(stat="identity")

# Figure 3-19
ggplot(cabbage_exp, aes(Date, Weight, fill = Cultivar)) +
  geom_bar(stat="identity", color="black") +
  guides(fill=guide_legend(reverse=TRUE)) +
  scale_fill_brewer(palette="Pastel1")

```

### Section 3.8. Making a Proportional Stacked Bar Graph

```{r}
ce <- ddply(cabbage_exp, "Date", transform, 
            percent_weight = Weight / sum(Weight) * 100)

# Figure 3-20
ggplot(ce, aes(Date, percent_weight, fill = Cultivar)) +
  geom_bar(stat="identity")

# Figure 3-21
ggplot(ce, aes(Date, percent_weight, fill = Cultivar)) +
  geom_bar(stat="identity", color="black") +
  guides(fill=guide_legend(reverse=TRUE)) +
  scale_fill_brewer(palette="Pastel1")
```

### Section 3.9. Adding Labels to a Bar Graph

```{r}
# Figure 3-22
ggplot(cabbage_exp, aes(interaction(Date, Cultivar), Weight)) +
  geom_bar(stat="identity") +
  geom_text(aes(label=Weight), vjust=1.5, color="white")
ggplot(cabbage_exp, aes(interaction(Date, Cultivar), Weight)) +
  geom_bar(stat="identity") +
  geom_text(aes(label=Weight), vjust=-0.2)

# Figure 3-23
ggplot(cabbage_exp, aes(Date, Weight, fill = Cultivar)) +
  geom_bar(stat="identity", position="dodge") +
  geom_text(aes(label=Weight), vjust=1.5, color="white",
            position=position_dodge(.9), size=3)

ce <- arrange(cabbage_exp, Date, Cultivar)
ce <- ddply(ce, "Date", transform, label_y=cumsum(Weight))

# Figure 3-24
ggplot(ce, aes(Date, Weight, fill = Cultivar)) +
  geom_bar(stat="identity") +
  geom_text(aes(y=label_y, label=Weight), vjust=1.5, color="white")

# Figure 3-25
ce <- arrange(cabbage_exp, Date, Cultivar)
ce <- ddply(ce, "Date", transform, label_y=cumsum(Weight)-0.5*Weight)
ggplot(ce, aes(Date, Weight, fill = Cultivar)) +
  geom_bar(stat="identity") +
  geom_text(aes(y=label_y, label=Weight), color="white")
```

### Section 3.10. Making a Cleveland Dot Plot

```{r}
# Figure 3-27
tophit <- tophitters2001[1:25, ]
ggplot(tophit, aes(avg, name)) +
  geom_point()

# Figure 3-28
ggplot(tophit, aes(avg, reorder(name, avg))) +
  geom_point(size = 3) +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x= element_blank(),
        panel.grid.major.y = element_line(color = "grey60", linetype="dashed"))
        
# Figure 3-29
ggplot(tophit, aes(reorder(name, avg), avg)) +
  geom_point(size = 3) +
  theme_bw() +
  theme(axis.text.x = element_text(angle=60, hjust=1),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x= element_blank(),
        panel.grid.major.y = element_line(color = "grey60", linetype="dashed"))

# Figure 3-30
nameorder <- tophit$name[order(tophit$lg, tophit$avg)]
tophit$name <- factor(tophit$name, levels=nameorder)
ggplot(tophit, aes(avg, name)) +
  geom_segment(aes(yend=name), xend=0, color="grey50") +
  geom_point(size=3, aes(color=lg)) +
  scale_color_brewer(palette="Set1", limit=c("NL", "AL")) +
  theme_bw() +
  theme(panel.grid.major.y = element_blank(),
        legend.position = c(1, 0.55),
        legend.justification = c(1, 0.5))


# Figure 3-31
ggplot(tophit, aes(avg, name)) +
  geom_segment(aes(yend=name), xend=0, color="grey50") +
  geom_point(size=3, aes(color=lg)) +
  scale_color_brewer(palette="Set1", limit=c("NL", "AL"), guide=FALSE) +
  theme_bw() +
  theme(panel.grid.major.y = element_blank()) +
  facet_grid(lg ~ ., scales = "free_y", space= "free_y")
        
```


<hr>
END!