---
title: "R Graphics Cookbook Chapter 4"
author: "Bowen W Jones"
date: "`r Sys.Date()`"
output: html_document
---

### Chapter 4. Line Graphs

```{r}
library(ggplot2)
library(gcookbook)
```

### Section 4.1. Making a Basic Line Plot

```{r}
# Figure 4-1
ggplot(BOD, aes(Time, demand)) +
  geom_line()

# Figure 4-2
ggplot(BOD, aes(factor(Time), demand)) +
  geom_line(group=1) +
  xlab("Time")

# Figure 4-3
ggplot(BOD, aes(Time, demand)) +
  geom_line() +
  ylim(0, max(BOD$demand))
```

### Section 4.2. Adding Point to a Line Graph

```{r}
# Figure 4-4
ggplot(BOD, aes(Time, demand)) +
  geom_line() +
  geom_point()

# Figure 4-5
ggplot(worldpop, aes(Year, Population)) +
  geom_line() +
  geom_point()
ggplot(worldpop, aes(Year, Population)) +
  geom_line() +
  geom_point() +
  scale_y_log10()
```

### Section 4.3. Making a Line Graph with Multiple Lines

```{r}
# Figure 4-6
library(plyr)
tg <- ddply(ToothGrowth, c("supp", "dose"), summarise, length=mean(len))
ggplot(tg, aes(dose, length, color = supp)) +
  geom_line()
ggplot(tg, aes(dose, length, linetype = supp)) +
  geom_line()

# Figure 4-7
ggplot(tg, aes(factor(dose), length, color = supp, group = supp)) +
  geom_line()

# Figure 4-8
ggplot(tg, aes(dose, length)) +
  geom_line()

# Figure 4-9
ggplot(tg, aes(dose, length, shape = supp)) +
  geom_line() +
  geom_point(size = 4)
ggplot(tg, aes(dose, length, shape = supp)) +
  geom_line() +
  geom_point(size = 4, shape = 21)

# Figure 4-10
ggplot(tg, aes(dose, length, shape = supp)) +
  geom_line(position = position_dodge(0.2)) +
  geom_point(position = position_dodge(0.2), size = 4)
```

### Section 4.4. Changing the Appearance of Lines

```{r}
# Figure 4-11
ggplot(BOD, aes(Time, demand)) +
  geom_line(linetype = "dashed", size = 1, color = "blue")

# Figure 4-12
ggplot(tg, aes(dose, length, color = supp)) +
  geom_line() +
  scale_color_brewer(palette = "Set1")
```

### Section 4.5. Changing the Appearance of Points

```{r}

```

### Section 4.6. Making a Graph with Shaded Areas

```{r}

```

### Section 4.7. Making a Stacked Area Graph

```{r}

```

### Section 4.8. Making a Proportional Stacked Area Graph

```{r}

```

### Section 4.9. Adding a Confidence Region

```{r}

```


<hr>
END!